\section{Hit these points}

The spread of heart disease and its ocnsequences in terms of mortality

How common are ICDs (nb implants per month in us and world)

market size

current practice for design and verification

heart+device as a hybrid system, based on cellular automata augmented with differential equations in the cells

in this paper, we show that $H_{CA}$ falls in a decidable class: stormed systems, and that approximate methods can be used to build a finite simulation.

our contributions:\\
theoretical\\
- show that the parallel composition of stormed is still stormed
\\
- show that approximate algorithms can produce a finite simulation (previous results use exact algo to produce a finite bisumulation)
\\
- the approximate reachability algo is more broadly applicable than manual polynomial approximations required in Vladimerou. especially since we have MANY models that might yield different polynomial approximations.
\\
application:\\
- show that the common components of most ICDs can be modeled as stormed
- show that a popular and practically validated heart model is stormed
- and there have been no examples of "real" stormed systems. This is the first such example.

there are no model checkers for stormed systems:
QE is too costly. 
the reachability-based algo is conceptual.
next research is to develop MCs for SHS.

SpaceEx approximations are o-minimal

why not just reachability? because want to verify LTL properties.

Examples of LTL properties of interest

the fact that we have timers in the state means we can indirectly verify some MTL properties: give examples

by Pfaffian extensions, can do any resolution of VTC.

Continuous extension of VTC: o-minimal by Pfaffian

the components we present are common to BSC, SJM, Biotronic and some MEdtronic so these results are broadly applicable.


---------------------------------------------------
0. Intro

The spread of heart disease and its ocnsequences in terms of mortality

How common are ICDs (nb implants per month in us and world)

market size

current practice for design and verification

related work: brihaye thesis, 
event b for cellular automata, hao's timed automata, PDE models of flavio and natalia, kwiatowska parameter synthesis, verification of tolerant systems (prabhakar), discrete abstraction of HS paper by pappas et al,
Kwiatowska's Invariant Verification of Nonlinear Hybrid Automata Networks of Cardiac Cells,
Grosu et al approimate bisim for sodium channel dynamics,
Mery's Formal VHM cellular automata model,
Pappas and girard's TAC09 paper

I. Theory

define transition system

define simulation nad bisimu for TS

give generic reachability algo for computing a bisimulation

define HS

define transition system of HS

define simulation and bisimulation for HS as TS

define o-minimal structures

define SS

show that using apx reachability on continuous systems yields a simulation

show that this simulation is finite

show that spaceex approximatino sets are o-minimal 

If initial partition is given by $x,y \in P$ iff $x \models p \leftrightarrow y \models p$, this respects formulas

show that parallel composition of SS is a SS


II. Modeling

basic cardiac EP 

cellular automata model of the heart with diff equations: 
	
	- give model
	
	- validated by EPs working with it to learn and by in vivo validation
	
	- show STORMED

APD restitution can also be part, see tech report

VT and SVT discrimination

Overview of detection algorithm

Three Consecutive Fast Intervals: show STORMED

VTC discrete: show STORMED

VTC continuous: show STORMED

Stability: show STORMED

We're skipping others

III Examples of properties




