\section{Composing STORMED systems}
\label{sec:compositionality}
The results in this section and the next apply to STORMED systems in general, including those with time-unbounded operation.
We write $[m] = \{1,\ldots,m\}$.
Given hybrid systems $\Sys_1,\ldots,\Sys_m$ in this section, $x^i, \guard^i, \theta^i,\ldots$ etc refer to a state, guard, flow $\ldots$ of system $\Sys_i$, $i\leq m$.
%
We show that the parallel composition of SHS is still a SHS.
Recall that $\theta_{\ell}(t;x)$ is the flow starting at $(\ell,x)$.
Given hybrid systems $\Sys_1,\ldots,\Sys_m$, their parallel composition $\Sys = \Sys_1 || \ldots ||\Sys_m$ is defined in the usual way:
$\Sys.\stSet = \Pi_i \stSet^i$,
$\Sys.\modeSet = \Pi_i \modeSet^i$,
$\Sys.\hsSet_0 =\Pi_i \hsSet_0^i$,
$Inv(\ell) = \Pi_{i}Inv^i(\ell^i)$,
$\theta_{\ell}(x,t)= [\theta_{\ell^1}^1(x^1,t)(t),\ldots,\theta_{\ell^m}^m(x^m,t)(t) ]^T$.
The system jumps if any of its subsystems jumps, so its guard sets are of the form 
$A^1\times\ldots \times A^m$ where for at least one $i$, $A^i$ is a guard of $\Sys_i$, and for the rest $A^j =\stSet^j$.
When a guard of a subsystem is satisfied, the state of that subsystem is reset according to its reset map.
The guards are made disjoint to avoid non-determinism.
\yhl{A system $\Sys$ is \emph{deterministic} if to every initial state $(\mode,\stPt)$, $\Sys$ produces a unique trajectory starting there.}

In general $\Sys$ is not separable: indeed for any candidate value of $d_{min}$, one could find a transition $(i,j)$ of $\Sys$ due to, say, a jump of $\Sys_1$, s.t. at that moment $x^2$ is closer than $d_{min}$ to one of its own guards, say $\guard^2_{(j^2,k^2)}$. 
This causes $\Sys$ to further jump $j \rightarrow k$ without having traveled the requisite minimum distance, thus violating the separability of $\reset_{ij}(\guard_{ij})$ and $\guard_{jk}$.
Therefore we need to impose an extra condition on minimum separability \emph{across} sub-systems.
\begin{thm}
	\label{thm:SHS composition}		
	Let $\SHS_i = (\Sys_i, \Ac, \phi^i,b^{i,-},b ^{i,+}, d_{min}^i, \varepsilon^i, \zeta^i)$, $i=1,\ldots,m$ be deterministic SHS 
	defined using the same underlying o-minimal structure, 
	and where each state space $\stSet^i$ is bounded by $B_{X^i}$.
	\\
	Define parallel composition $\SHS = (\Sys, \Ac, \phi,b^-,b^+, d_{min}, \varepsilon, \zeta)$ where
	$\Sys = \Sys_1 || \ldots ||\Sys_m$,	
	$\phi = (\phi^1,\ldots,\phi^m)^T \in \Re^{mn}$,
	$b^{i,-} = \inf_{x \in \stSet} \phi\cdot x$,
	$b^{i,+} = \sup_{x \in \stSet} \phi\cdot x$,
	$\varepsilon = \min(\min_i \varepsilon^i, \min_i \frac{\zeta^i}{B_{X^i}})$,
	$\zeta = \min_i \zeta^i$ and
	\[d_{min} = \min_{I\subset [m]} (\min_{i\in I}d_{min}^i, \min_{i\in I ,j \in [m]\setminus I }d_{min}^{ij})\]	
	Assume that the following \textbf{Collection Separability} condition holds: 	
	\yhl{for all $i,j \leq m, \neq j $ there exists $d_{min}^{ij}>0$ s.t. 
		\yhl{if $\stPt \in \stSet$ is in the reachable set of $\Sys$} and 
		$x^i \in G^i_e \land x^j \notin G^j_{e'} \; \forall e' \in E^j$ 
		then $d(x^j,G^j_{e'}))>d_{min}^{ij}$ for all $e'\in E^j$ 
		where $E^j$ is the edge set of $\SHS_j$ and $G^j_{e'}$ is a guard of $\SHS_j$ on edge $e' \in E^j$.}
	Then $\SHS$ is STORMED.
\end{thm}
\begin{prf}
\textbf{(S)} In $\Sys$, let $y=(y^1,\ldots,y^m)=\reset_e((x^1,\ldots,x^m))$ and assume that it was $\Sys_1$ that caused the jump.
Thus $y^j=x^j,j >1$.
Write $e=(\mode,\mode ')$.
By Collection Separability,  $d(y^j,G^j_{e^j})>d_{min}^{1j}$ for all $j>1,e^j\in E^j$, 
and by separability of $\Sys_1$ $d(y^1,G^1_{e^1}) > d_{min}^1$ for all $e^1 \in E^1$.
So by $d(y,G_{\mode', \mode ''}) > \min (d_{min}^1, \min_{j>1}d_{min}^{1j}) > d_{min}$ for any guard leading out of $\mode'$, and we have separability.
The argument can be repeated for any subset $I \subset [m]$ of systems jumping simultaneously.
\\
\textbf{(T)}:
The $\Sys$ flow $\theta_\mode(t;x)$ is TISG because the component flows $\theta^i_{\mode^i}(t;x^i)$ are TISG.
\\
\textbf{(O)} The cartesian product of definable sets is definable, so the system $\Sys$ is o-minimal.
\\
\textbf{(RM)} First we show that resets of $\Sys$ are monotonic, then that the flows of $\Sys$ are monotonic.
Let $p,q \in \modeSet$ be two modes of $\Sys$, $p\neq q$.

\underline{Case 1: $\Sys$ jumps $p \rightarrow p$}.
So any subsystem $\Sys_i$ either jumped $p^i \rightarrow p^i$ or didn't jump at all.
If $x^+ = x^-$, then (RM) is satisfied.
Else, define $\phi \defeq (\phi^1,\ldots,\phi^m) \in \Re^{n\cdot m}$, where $\phi^i$ is the $\phi$ vector of system $\Sys_i$.
Then $\phi \cdot (x^+ - x^-) = \sum_{i\in K}\phi^i\cdot(x^{i,+} - x^{i,-})$, 
where $K \subset [m]$ is the set of indices of sub-systems that jumped with $x^{i,-} \neq x^{i,+}$.
Note that $K$ depends on $x^-,x^+$.
%
For all $x^-,x^+$ pairs (and so for all $K$) 
$\sum_{i\in K} \zeta^i \geq \min_{i \in [m]}\zeta^i \defeq \zeta > 0$.
So by (RM) for each $\Sys_i$,
\begin{equation*}
\label{eq:parallel rm1}
\phi \cdot (x^+ - x^-) =  \sum_{i\in K}\phi^i\cdot(x^{i,+} - x^{i,-}) \geq \sum_{i\in K}\zeta^i \geq \zeta > 0
\end{equation*}
Thus (RM) is satisfied.

\underline{Case 2: $\Sys$ jumps $p \rightarrow q$}.
At least one syb-system $\Sys_i$ jumped $p^i \rightarrow q^i \neq p^i$.
Then 
$\phi \cdot (x^+ - x^-) = \sum_{i\in [m]}\phi^i\cdot(x^{i,+} - x^{i,-}) = \sum_{i\in K}\phi^i\cdot(x^{i,+} - x^{i,-})$,
where $K = K_= \cup K_{\neq} \subset [m]$ and 
$K_=$ is the index set of subsystems that jumped $p^i \rightarrow p^i$ with $x^{i,+} \neq x^{i,-}$, 
and $K_{\neq}$ is the index set of subsystems that jumped $p^i \rightarrow q^i \neq p^i$ with $x^{i,+} \neq x^{i,-}$.
Subsystems that didn't jump or jumped without changing their continuous state don't contribute to the sum.
Note that $K_=,K_{\neq}$ depend on $x^-,x^+$.
So we have
$\phi \cdot (x^+ - x^-) \geq \sum_{i\in K_{\neq}}\varepsilon^i ||x^{i,+} - x^{i,-}|| + \sum_{i\in K_=} \zeta^i$.

For all $X^i$, $||x^{i,+} - x^{i,-}|| \leq B_{X^i}$ for all $x^{i,-},x^{i,+} \in X^i$.
Therefore $\zeta^i \frac{||x^{i,+} - x^{i,-}||}{B_{X^i}} \leq \zeta^i$ for all $i\in K$.
So 
\begin{eqnarray*}
&&	\phi \cdot (x^+ - x^-) \geq
\\ 
&\;&\sum_{i\in K_{\neq}} (\min_{i\in [m]}\varepsilon^i) ||x^{i,+} - x^{i,+}|| + \sum_{i\in K_=} \frac{\zeta^i}{B_{X^i}}||x^{i,+} - x^{i,-}|| \geq 
\\
&& \sum_{i\in K_{\neq}} (\min_{i\in [m]}\varepsilon^i) ||x^{i,+} - x^{i,-}|| + \sum_{i\in K_=} (\min_{i\in [m]}\frac{\zeta^i}{B_{X^i}})||x^{i,+} - x^{i,-}||
\end{eqnarray*}
Let $\varepsilon \defeq \min(\min_i \varepsilon^i, \min_i \frac{\zeta^i}{B_{X^i}})$.
Then 
\begin{equation*}
\phi \cdot (x^+ - x^-) \geq \sum_{i\in K} \varepsilon ||x^{i,+} - x^{i,-}|| \geq \varepsilon ||x^+-x^-||
\end{equation*}
So $\Sys$ has monotonic resets.

%What about $\Sys$?
%Consider again the case where $\Sys$ jumps $p\rightarrow q\neq p$, the other case being trivial.
%Fix an arbitrary $\phi_d \leq - \varepsilon$.
%Let $\hx = (\stPt,\mode)$ be the state of $\widehat{\Sys}$, and let $\hat{\phi} = (\phi,\phi_d)$ with $\phi= (\phi_1,\ldots,\phi_m)$ as defined above.
%Then $\hat{\phi} \cdot (\hx^+ - \hx^-) = \phi \cdot (x^+ - x^-) + \phi_d \cdot (q-p) \geq \varepsilon ||x_i^+-x_i^-|| + \phi_d (1-|\modeSet|) \geq  \varepsilon ||x_i^+-x_i^-|| + \varepsilon (|\modeSet|-1) \geq  \varepsilon ||x_i^+-x_i^-|| + \varepsilon |q-p|$ and the resets of $\widehat{\Sys}$ are monotonic.
%
The flows of $\Sys$ are also monotonic along $\phi$.
Indeed for any $q \in \modeSet$,
$\phi\cdot (\theta_q(t+\tau;x) - \theta_q(t;x) ) = \sum_{i=1}^{m}\phi^i \cdot (\theta^i_{q^i}(t+\tau;x^i) - \theta^i_{q^i}(t;x^i)) \geq \sum_i \varepsilon^i ||(\theta^i_{q^i}(t+\tau;x^i) - \theta^i_{q^i}(t;x^i))|| \geq \varepsilon ||(\theta_{q}(t+\tau;x) - \theta_{q}(t;x))||$

\textbf{(ED)} By Prop. \ref{prop:ED}.
	\end{prf}